Empirical normative theories

### 2020-07-25 simple.tex
Drop minimal attacking coalitions, for simpler definitions and a much simpler proof.

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Define $\df \subseteq \allargs × \alldargs$ as $\df = \dbeatsinv \circ \gbeatsinv$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
An empirical theory must satisfy
$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.

@@

Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$. 
Define $\args \ibeatscoalstr \ar_0$ iff $\forall \hist \in \allhist: [\hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0] ⇒ \hist \nileadstost \phi$, that is, iff no $\hist$ that end with $\args$ followed by $\ar_0$ lead to $\phi$.
Note that $\forall \ar_0 \in \allargs, \args \subseteq \gbeatsinv(\ar_0): \args \ibeatscoalstr \ar_0 ⇒ \args \ibeatscoal \ar_0$. That is because $\ar_0 \ngbeats \ar_0$, because $\gbeats$ is irreflexive by definition of an empirical theory, and thus suffices to consider any sequence of arguments $\hist$ using only and all the arguments $\args \cup \set{\ar_0}$ and placing $\ar_0$ last: because $\args \ibeatscoalstr \ar_0$, $\hist \nileadstost \phi$, and the existence of $\hist$ proves that $\args \ibeatscoal \ar_0$.

Given $i \in I, \phi \in \Phi$ and $\ar_0, \ar_1 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \ar_1 \in \args \land \args \ibeatscoal \ar_0 \land \args \setminus \set{\ar_1} \nibeatscoalstr \ar_0$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsinv}](\ar)$. Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

@@

\begin{remark}
	I need the following two facts. 1) If $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \args \ibeats \ar_0$. 2) Proving that $\ar_2 \in \gargs$ is easy enough, thus, if $\args = \set{\ar_1, \ar'_1}$ is minimal for $\args \ibeats \ar_0$, then, showing $\exists \hist = (…, \ar_1, \ar_0) \ileadstost \phi, \ar'_1 \notin \hist$ (and the same inverting $\ar_1$ and $\ar'_1$), is enough.

	Problem happens in the following case. $\ar'_1$ alone is uncertain, meaning $\exists \hist = (… \ar'_1 … \ar_0) \nileadstost \phi$ and $\exists \hist = (…, \ar'_1, \ar_0) \ileadstost \phi$. Then, a counter-theory $\delta$ may claim that $\ar'_1$ alone is ineffective: suffice to show the example $(…, \ar'_1, \ar_0) \ileadstost \phi$. Whereas in fact $\ar'_1$ alone is sometimes effective. Then, $\args = \set{\ar_1, \ar'_1}$ may be claimed to be effective by combination effect (and $\ar'_1$ can’t be blamed, although it should, as $\delta$ has “proven” it ineffective). Thus, $\ar_2$, defending against $\ar_1$, ends up in $\gargs$. Assume $\ar_1$ is innocuous for $i$ (otherwise, no problem, as $\ar_2$ is legitimate) ($\ar_1$ could be efficient for others than $i$, which justifies $\ar_1 \gbeats \ar_0$). Then $\ar_2$ shouldn’t be played, it is only included as a result of the weak demand about proving that $\ar'_1$ is ineffective.

Note that if we agree that $\ar'_1$ is uncertain, then $\gamma$ should play $\ar'_2$ to answer the coalition $\args$ attack (as required even without the coalitions definition), not $\ar_2$. But this conflicts with the formal definitions. Note that if $\ar'_1$ is known as uncertain for everybody, there is no problem, as $\gamma$ should include $\ar'_2$ from the start. Problem happens if $\ar'_1$ is suspected uncertain for some and inefficient for others.

	Here is a similar problem: assume $\ar_1$ and $\ar'_1$ are uncertain for some and innocuous for others (not necessarily the same). Assume we observed $(…, \ar_1, \ar_0) \ileadstost \phi$ (without $\ar'_1$) and $(…, \ar'_1, \ar_0) \ileadstost \phi$ (without $\ar_1$, and imagining this would be possible to know); but $\set{\ar_1, \ar'_1}$ attacks $\ar_0$. Then we ignore whether, for $i$, $\ar_1$ or $\ar'_1$ is innocuous; and thus ignore whether $\ar_2$ or $\ar'_2$ should be played. The right answer is probably: play $\ar_2 + \ar'_2$. In fact, suffices to assume that, whenever such situation can happen, $\gamma$ has planned that $\ar_2$ be attacked by $\ar'_1$, and conversely, and then we get immediately that $\ar_2 + \ar'_2$ is involved. (But also that $\ar_2$ should be defended, whereas this is perhaps too demanding?)
\end{remark}

@@

	Lemma. Given any $\ar_0$ that $i$-defends $\phi$, $\forall \args \subseteq \gbeatsinv(\ar_0): [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$. Observe that the implication holds for $\args = \emptyset$, because $\emptyset \nibeatscoal \ar_0$ as $\ar_0$ $i$-defends $\phi$. Now, given $k \in \N$, assume that $\forall \args \subseteq \allargs \suchthat \card{\args} = k: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$, and let us show that $\forall \args \subseteq \allargs \suchthat \card{\args} = k + 1: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
	Consider $\args \subseteq \allargs \suchthat \card{\args} = k + 1 \land \args \ibeatscoal \ar_0$. One of the following two cases hold. First case: $\forall \args' \subset \args \suchthat \card{\args'} = k: \args \nibeatscoalstr \ar_0$. Then, $\forall \ar_1 \in \args: \ar_1 \ibeats \ar_0$. Second case: $\exists \args' \subset \args \suchthat \card{\args'} = k \land \args' \ibeatscoalstr \ar_0$. Then, $\args' \ibeatscoal \ar_0$ (recalling that ${\ibeatscoalstr} \subseteq {\ibeatscoal}$ and using the contrapositive), thus $\exists \ar_1 \in \args' \suchthat \ar_1 \ibeats \ar_0$ (using the induction hypothesis), hence, $\exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.

	This lemma permits to deduce that, given $\ar_0$ that $i$-defends $\phi$, $\hist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$, and $\args = \gbeatsinv(\ar_0) \cap \hist$: $\args ≠ \emptyset ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$. This holds because in that case, $\args \ibeatscoal \ar_0$.

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeats \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
	Define $\args = \gbeatsinv(\ar_0) \cap \hist$.
	Because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
	From the preceding conclusion, $\exists \ar_1 \in \args \suchthat \ar_1 \gbeats \ar_0$ and $\ar_1 \ibeats \ar_0$.
	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \alldargs \suchthat \ard_2 \dbeats \ar_1$. Defining $\ar_2 = \ar_0 + \ard_2$, $\ar_2 \in \dip(\ar_0)$ by definition of $\dip$.

	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering $\ard_2$ and $\ar_2$ as defined in the lemma, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ard_2 \in \df(\ar_0)$ by definition of $\df$.

	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs[i, \phi]$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

@@

	Better first simplify the related definitions in the “normal” case.
\end{remark}

@@

\section{Empirical theories}
\subsection{Simple to complex}
From an additive single-answer empirical theory, we can define a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard_2 \suchthat \ard_2 \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise. Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard_2 \in \allargs \suchthat \ard_2 \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2}$.
Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
\commentOC{Could be false.}

Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0), (\ard_6, \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard_2 = \ar_4 + \ard_6$, then $f^{-1}(\ar_0 + \ard_2) = f^{-1}(\ar_4 + \ard_6) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard_2) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$. Consider ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard_2$. Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.

>>>>

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Given $\ar \in \allargs$, define $\df(\ar) \subseteq \powersetz{\alldargs}$ as $\df(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)}$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
Given any $\ar \in \allargs$ and $\dargs \in \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
Define $\dfp \subseteq \allargs × \allargs$ as $\forall \ar \in \allargs: \dfp(\ar) = \set{\ar + \dargs \suchthat \dargs \in \df(\ar)}$.

\begin{remark}
	Equivalently, $\df(\ar_0) = \powersetz{\dbeatsinv \circ \gbeatsinv}$. First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$. Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$. That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{remark}

An empirical theory must satisfy
$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.

@@

Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeatscoal \ar_0}$. 
Observe that $\di(\ar) \subseteq \df(\ar)$.
Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

@@

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \dargs \in \di(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeatscoal \ar_0$.
	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
	Therefore, $\dbeatsinv(\args) \in \di(\ar_0)$.

	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering any $\dargs \in \di(\ar_0)$ and $\ar_2 = \ar_0 + \dargs$, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ar_2 \in \dfp(\ar_0)$ because $\dargs \in \di(\ar_0) ⇒ \dargs \in \df(\ar_0)$.

	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs[i, \phi]$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

@@

	Better first simplify the related definitions in the “normal” case.

	Consider extending $\histend$ with $\zar$ to have $\zar \in \histend$.
\end{remark}

@@

\section{Empirical theories}
\subsection{Simple to complex}
From an additive single-answer empirical theory, we can define a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard \suchthat \ard \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise. Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard \in \allargs \suchthat \ard \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard}$.
Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
\commentOC{Could be false.}

Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard, \ar_1), (\ar_1, \ar_0), (\ard[6], \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard = \ar_4 + \ard[6]$, then $f^{-1}(\ar_0 + \ard) = f^{-1}(\ar_4 + \ard[6]) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$. Consider ${\gbeats} = \set{(\ard, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard$. Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.
